Supplementary Methods

### 2020-05-23 body.tex
Revise abstract

Now, fifteen years later, NumPy underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2020scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It is a community-developed, open-source library, which provides a
multidimensional Python array object along with array-aware functions
that operate on it.
Because of its inherent simplicity, the NumPy array is
the \emph{de facto} exchange format for array data in Python.

>>>>

Now, fifteen years later, NumPy underpins almost every Python library that does scientific or
numerical computation \cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}
including SciPy \cite{virtanen2020scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It is a community-developed, open-source library, which provides a
multidimensional Python array object along with array-aware functions
that operate on it.
Because of its inherent simplicity, the NumPy array is
the \emph{de facto} exchange format for array data in Python.

### 2020-05-23 summary.tex
Revise abstract

% - 2-3 sentences of basic-level introduction to the field;
Array programming provides a powerful, compact, expressive syntax for accessing,
manipulating, and operating on data in vectors, matrices, and
higher-dimensional arrays \cite{iverson1980notation}.
% - a brief account of the background and rationale of the work;
NumPy is the primary array programming library for the Python language
\cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
It plays an essential role in research analysis pipelines in fields as
diverse as physics, chemistry, astronomy, geoscience, biology, psychology,
material science, engineering, finance, and economics.
For example, in astronomy, NumPy was an important part of the software stack used
in the discovery of gravitational waves \cite{abbott2016observation}
and the first imaging of a black hole \cite{eht-imaging}.
% - a statement of the main conclusions (introduced by the phrase 'Here we show' or its equivalent);
Here we show how a few fundamental array concepts lead to a simple and
powerful programming paradigm for organizing, exploring, and analyzing
scientific data.
% - 2-3 sentences putting the main findings into general context so it is
%   clear how the results described in the paper have moved the field forwards.
NumPy is the foundation upon which the entire scientific Python
universe is constructed. It is so pervasive that several projects,
targeting audiences with specialized needs, have developed their own
NumPy-like interfaces and array objects. Because of its central position in the
ecosystem, NumPy increasingly plays the role of an interoperability layer
between these new array computation libraries.

>>>>

% - 2-3 sentences of basic-level introduction to the field;
Array programming provides a powerful, compact, expressive syntax for accessing,
manipulating, and operating on data in vectors, matrices, and
higher-dimensional arrays. % \cite{iverson1980notation}.
% - a brief account of the background and rationale of the work;
NumPy is the primary array programming library for the Python language.
%\cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
It plays an essential role in research analysis pipelines in fields as
diverse as physics, chemistry, astronomy, geoscience, biology, psychology,
material science, engineering, finance, and economics.
For example, in astronomy, NumPy was an important part of the software stack used
in the discovery of gravitational waves% \cite{abbott2016observation}
and the first imaging of a black hole. % \cite{eht-imaging}.
% - a statement of the main conclusions (introduced by the phrase 'Here we show' or its equivalent);
Here we review how a few fundamental array concepts lead to a simple and
powerful programming paradigm for organizing, exploring, and analyzing
scientific data.
% - 2-3 sentences putting the main findings into general context so it is
%   clear how the results described in the paper have moved the field forwards.
NumPy is the foundation upon which the entire scientific Python
universe is constructed. It is so pervasive that several projects,
targeting audiences with specialized needs, have developed their own
NumPy-like interfaces and array objects. Because of its central position in the
ecosystem, NumPy increasingly plays the role of an interoperability layer
between these new array computation libraries.

%Reviews start with a 200-word maximum abstract, which should set the stage and
%end with a summary sentence.
%This abstract cannot include references, and it's important that it makes
%it clear that this article is a Review article.
